---
title: "IDR stuff"
format: html
editor: visual
---

```{r setup}
pacman::p_load(
  tidyverse,
  janitor,
  MASS,
  car
)
```

## Descriptives

Are OAscores from one pop or a mixture of pops?

```{r}
db_j_exp <- db_j %>%
  unnest(x_concepts) %>%
  select(-id,-wikidata) %>%
  filter(level < 2) %>%
  rename(concept = display_name,
         concept_score = score) %>%
  filter(concept != "Combinatorial chemistry")

concepts %>%
  filter(display_name != "Combinatorial chemistry") %>%
  transmute(concept = display_name,
            related_concepts,
            c_level = level) %>%
  unnest(related_concepts) %>%
  filter(level < 2) %>%
  select(
    concept,
    c_level,
    related_concept = display_name,
    r_level = level,
    score) %>%
  mutate(relation_type =
           case_when(
             (c_level == 0 & r_level == 0) ~ "High level",
             (c_level == 1 & r_level == 1) ~ "Low level",
             TRUE ~ "Middle level"
           ) %>% factor(c("High level",
                           "Middle level",
                           "Low level"))
         )-> concepts_ext
```

Visualise how score is strongly dependent on the type of relation

(eg. English and Literature same as Organic and Inorganich Chemistry)

```{r}
concepts_ext %>%
  ggplot() +
  geom_density(aes(x = score,
                   fill = relation_type),
            position = "stack"
  )
```

Normalisation

```{r}
concepts_ext %>%
  mutate(score = score - mean(score),
         .by = relation_type) %>%
  mutate(
    score = score + abs(min(score)),
    score = score / max(score), 
    score_rank = score %>% rank() / n()) %>% View()
  ggplot() +
  geom_density(aes(x = score,
                   fill = relation_type),
            position = "stack"
  )
```

## Research Questions

### Do WoS have same average IDR level if one computes a fast-IDR measure on the conceptual scores of OpenAlex?

#### Method: For each discipline (list of journals) on both WoS and Scopus is applied a IDR measure based on the summes OA scores multiplied per the number of papers of the journal.

Prepare the database:

```{r}

concepts %>%
  filter(display_name != "Combinatorial chemistry") %>%
  transmute(concept = display_name,
            related_concepts) %>%
  unnest(related_concepts) %>%
  filter(level < 2) %>%
  select(
    concept,
    related_concept = display_name,
         score) %>%
  mutate(score = score/max(score)) %>%
  adorn_rounding(4) %>%
  pivot_wider(names_from = related_concept,
              values_from = score,
              values_fill = 0
              ) %>%
  arrange(concept) %>%
  select(concept, sort(names(.)[-1])) %>%
  select(-concept) %>%
  as.matrix() -> concepts_matrix


colnames(concepts_matrix) -> row.names(concepts_matrix)

concepts_matrix %>% isSymmetric.matrix()
```

1# WoS Areas

```{r}
db_j_exp %>%
  separate_longer_delim(WoS_Area, "; ")
```

```{r}
journals %>%
  select(counts_by_year,display_name) -> assign

View(assign)
```
