---
title: "Sampling from OA"
author: "GG Cantone"
date: "2023-06-02"
output:
---

In case you have not the package manager `pacman`, install it.

```{r}
install.packages(pacman)
```

Setup

```{r setup, include=FALSE}
pacman::p_load(
  tidyverse,
  openalexR,
  readr,
  readxl,
  janitor,
  ggExtra,
  rvest
)
```

---

WOS

Importing WOS

```{r}
read_csv("Scientific.csv") %>%
  add_row(read_csv("Social_Sciences.csv")) %>%
  select(-`Publisher address`) %>%
  distinct(`Journal title`,
           .keep_all = T) %>%
  pivot_longer(cols = c("ISSN","eISSN"),
               names_to = "Type",
               values_to = "ISSN"
  ) %>%
  select(-Type) %>%
  distinct(`Journal title`,
           .keep_all = T) %>%
  rename(WoS_JSC = `Web of Science Categories`,
                     main_issn = ISSN
                     ) %>%
  mutate(WoS_JSC = WoS_JSC %>%
                       str_replace(
                         "Women'S Studies",
                         "Women Studies")) %>%
  select(main_issn,WoS_JSC, Languages)-> WoS_j
```

Mapping WoS SC and Areas

```{r}
WoS_categories <- read_delim("WoS_categories.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE) %>%
  select(Category,Group) %>%
  distinct() %>%
  mutate(Category =
           Category %>% str_to_title() %>%
           str_replace_all(",",", "),
         Group =
           str_replace_all(Group, "\\|","; ")
         ) -> WoS_SC


```

Integrating SCJ and Areas

```{r}
WoS_j %>%
  mutate(WoS_JSC =
           WoS_JSC %>%
           str_replace_all(" \\| ","; ")
         ) %>%
  separate_rows(WoS_JSC,sep = "; ") %>%
  left_join(WoS_SC %>% rename(WoS_JSC = Category,
                              WoS_Area = Group)) %>%
  group_by(across(-c("WoS_JSC","WoS_Area"))) %>%
  summarise(
    WoS_JSC = str_c(WoS_JSC, collapse = "; "),
    WoS_Area = str_c(WoS_Area, collapse = "; ")
  ) %>%
  ungroup() %>%
  mutate(
    WoS_Area =
      map_chr(
        str_split(WoS_Area, "; "),
        ~ str_c(unique(.x),
                collapse = "; ")
        )
    )-> WoS_j
```


---

SCOPUS

Scraping Scopus Categories

```{r}
read_html("https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/") %>%
  html_elements(xpath="//td | //th") %>%
  html_text() %>%
  .[4:1005] -> Scopus_codes

tibble(
  Code = Scopus_codes[seq(1, length(Scopus_codes), by = 3)],
  Subject = Scopus_codes[seq(2, length(Scopus_codes), by = 3)],
  Field = Scopus_codes[seq(3, length(Scopus_codes), by = 3)]
  ) %>%
  mutate(
  Area = str_sub(Code, start = 1, end = 2) %>%
    case_match(
      "10" ~ "General",
      "11" ~ "Agricultural and Biological Sciences",
      "12" ~ "Arts and Humanities",
      "13" ~ "Biochemistry, Genetics and Molecular Biology",
      "14" ~ "Business, Management and Accounting",
      "15" ~ "Chemical Engineering",
      "16" ~ "Chemistry",
      "17" ~ "Computer Science",
      "18" ~ "Decision Sciences",
      "19" ~ "Earth and Planetary Sciences",
      "20" ~ "Economics, Econometrics and Finance",
      "21" ~ "Energy",
      "22" ~ "Engineering",
      "23" ~ "Environmental Science",
      "24" ~ "Immunology and Microbiology",
      "25" ~ "Materials Science",
      "26" ~ "Mathematics",
      "27" ~ "Medicine",
      "28" ~ "Neuroscience",
      "29" ~ "Nursing",
      "30" ~ "Pharmacology, Toxicology and Pharmaceutics",
      "31" ~ "Physics and Astronomy",
      "32" ~ "Psychology",
      "33" ~ "Social Sciences",
      "34" ~ "Veterinary",
      "35" ~ "Dentistry",
      "36" ~ "Health Professions"
  )
  ) -> Scopus_codes
```

Importing Scopus categories

```{r}

Scopus_db <- read_excel("Scopus_db.xlsx") %>%
  transmute(ISSN = `Print-ISSN`,
            eISSN = `E-ISSN`,
            Active = `Active or Inactive`,
            Type = `Source Type`,
            Scopus_Citescore = CiteScore %>% as.numeric(),
            Codes = `All Science Journal Classification Codes (ASJC)` %>%
              str_sub(end = -2)
) %>%
  filter(Type == "Journal",
         Active == "Active"
         )


Scopus_db %>%
  pivot_longer(1:2,
               values_to = "ISSN") %>%
  distinct(ISSN, .keep_all = T) %>%
  select(-name) %>%
  filter(!ISSN %>% is.na()) %>%
  mutate(Scopus_JSC =
           str_replace_all(Codes,
                           setNames(Scopus_codes$Subject, Scopus_codes$Code)),
         Scopus_Area =
           str_replace_all(Codes,
                           setNames(Scopus_codes$Area, Scopus_codes$Code)),
         Scopus_Area =
           map_chr(
             str_split(Scopus_Area, "; "),
             ~ str_c(unique(.x),
                     collapse = "; "))
         
         ) %>%
  transmute(main_issn = ISSN,
            Scopus_JSC,
            Scopus_Area,
            Scopus_Citescore) -> Scopus_db

```


---

OPENALEX

Sampling all concepts

```{r}
oa_fetch(
  entity = "concepts",
  level = c(0:1)
) -> concepts

concepts %>%
  count(level) -> OA_concepts

OA_concepts %>%
  rename(concept = display_name,
         rel=related_concepts) %>%
  select(concept,
         level,
         rel) %>%
  unnest(rel,
         names_sep = "_") %>%
  rename(rel_concept = rel_display_name) %>%
  select(concept,
         level,
         rel_id,
         rel_concept,
         rel_level,
         rel_score,
         ) %>%
  filter(rel_level <2)  -> OAc_proximity
```


Download OpenAlex data on journals

```{r}
oa_fetch(
  entity = "venues",
  issn = WoS_j$ISSN
) -> journals
```

---

Database consolidation: joins of categories

Join WoS
```{r}
journals %>%
  transmute(id_j = id,
         journal = display_name,
         main_issn = issn_l %>% as.character(),
         n_papers = works_count,
         x_concepts) %>%
  left_join(WoS_j) %>%
  filter(!WoS_JSC %>% is.na(),
         !WoS_Area %>% is.na(),
         !x_concepts %>% is.na()) -> db_j
```

Join Scopus

```{r}
db_j %>%
  mutate(main_issn = main_issn %>%
           str_replace_all("[^[:alnum:] ]", "")) %>%
  left_join(Scopus_db) %>%
  filter(!Scopus_JSC %>% is.na(),
         !Scopus_Area %>% is.na()
         )-> db_j
```

---

## 

Sample papers

```{r}
oa_fetch(
  entity = "works",
  primary_location.source.id = db_j$id_j,
  abstract = F,
  publication_year = c(2012,2015,2018),
  type = "journal-article",
  options = list(sample = 10)
) -> sample


oa_fetch(
  entity = "works",
  primary_location.source.id = db_j$id_j[runif(50,
                                               0,
                                               nrow(db_j))],
  abstract = F,
  publication_year = c(2012,2015,2018),
  type = "journal-article",
#  options = list(sample = 15000)
) -> sample
```

List of referenced papers in the sample

```{r}
smpl_rl = sample %>%
  select(display_name, referenced_works) %>%
  unnest(referenced_works) %>%
  distinct(referenced_works) %>%
  pull(referenced_works)

smpl_rl[3]
```

